Reionization Planck 2018 Notes

### 2020-07-30 results/notes.tex

\begin{figure}
\includegraphics[width=0.65\textwidth]{getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_gauss_smoothed_tanh_std_0p0067.png}
\label{fig:}
\caption{Gaussian convolving the direct MCMC 1D distribution by hand with f = 0.14 where the original standard deviation is set to 0.0067. This corresponds to the right side of asymmetric distribution from the original MCMC $\tau = 0.0591 + 0.0055 - 0.0067$.
} 
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_gauss_smoothed_tanh_std_0p0055.png}
\label{fig:}
\caption{Gaussian convolving the direct MCMC 1D distribution by hand with f = 0.14 where the original standard deviation is set to 0.0055. This corresponds to the left side of asymmetric distribution from the original MCMC $\tau = 0.0591 + 0.0055 - 0.0067$.
} 
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_gauss_smoothed_tanh_std_0p0067.png}
\label{fig:}
\caption{Gaussian convolving the direct MCMC 1D distribution by hand with f = 0.14 where the original standard deviation is set to 0.0067. This corresponds to the right side of asymmetric distribution $\tau = 0.0591 + 0.0055 - 0.0067$ from the original MCMC.
} 
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_gauss_smoothed_tanh_std_0p0055.png}
\label{fig:}
\caption{Gaussian convolving the direct MCMC 1D distribution by hand with f = 0.14 where the original standard deviation is set to 0.0055. This corresponds to the left side of asymmetric distribution $\tau = 0.0591 + 0.0055 - 0.0067$ from the original MCMC.
} 
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/getdist_smoothing_test/pl18_pc_zmax30_pliklite_srollv2_1015_tau_posterior_python_kde_f_0p1_vs_0p14.png}
\label{fig:}
\caption{Comparing f = 0.10 and f = 0.14 lines from python KDE - to see that f = 0.14 is indeed more smoothed than f = 0.10 as expected.
} 
\end{figure}

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_1600.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_800.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_100.png

results/cosmomc_kde/getdist_smoothing_test/pl18_relike_tanh_tau_dz0p5_1D_smooth_scale_1D_2_num_bins_1D_50.png
